\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter

%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\textbf{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#4}\\
\descript{#2}\hspace*{\fill}  \location{#3} \fakeNewLine\\}

% Create project heading. Parameters: Name, link, Tech stack
\newcommand{\projectHeading}[3]{\Project{#1}{#2}
\descript{#3}\\}

\newcommand{\projectHeadingWithDate}[4]{\Project{#1}{#2}
\descript{#3 | #4}\\}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\cgpa}[1]{\textbf{Cum. GPA:} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Sayan Hazra}
% How you want it to show up on the resume
\newcommand{\yourWebsite}{codechef/mrsayan}

\newcommand{\yourWebsiteLink}{https://www.codechef.com/users/mrsayan}
\newcommand{\yourEmail}{iamsayan568@gmail.com}
\newcommand{\yourPhone}{+91-7278477569}
\newcommand{\githubUserName}{mrsayan}
\newcommand{\linkedInUserName}{mrsayan}

\begin{center}
    \Huge \scshape \latoRegular{\yourName} \\ \vspace{1pt}
    \small \href{mailto:\yourEmail}{\underline{\yourEmail}}  $|$  \yourPhone $|$ 
    \href{https://www.linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}} 
    $|$ \href{\yourWebsiteLink}{\underline{\yourWebsite}}
     
    
\end{center}

%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
\educationHeading{B. Tech.  Computer Science and Engineering }{Kalinga Institute of Industrial Technology}{Bhubaneswar, Odisha}{Sept’ 20 - Aug’ 24 (Expected)}

\cgpa{8.73/10}
% \courseWork{Data Structures and Algorithms; Operating Systems;  Computer Security; Software Testing; Advanced Networking; Big Data Analytics}
\sectionsep

%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}

\resumeHeading{\href{https://www.linkedin.com/company/pegman/}{PEGMAN}}{Backend Engineering - Intern}{Remote}{Aug 2023 – Present}
\begin{bullets}
    \item Designed the system architecture for \textbf{delivery engine}, empowering the platform as users' doorstep Liquor Delivery.
    % \item Devised optimal approaches, achieving \textbf{99.8 percent} crash-free user sessions making it highly scalable and available.
    \item Developed \textbf{8+ endpoints} across \textbf{2 microservices} integrating with \textbf{OMS} and \textbf{Aadhaar API} for e-KYC Verification.
    \item  Engaged in product/design discussions, offering valuable \textbf{insights to impact} product development, user satisfaction.
    % \item  Applied a customer-first approach aligning strategies with their goals  to ensure the pain points are addressed.
\end{bullets}
\sectionsep

\resumeHeading{\href{https://drive.google.com/file/d/14vUDJCzvPunc1eGmI0NPFkZmzR82nggh/view?usp=drive_link/}{HIGHRADIUS}}{Product Engineering - Intern}{Remote}{May 2023 - Jul 2023}
\begin{bullets}
    \item Built an \textbf{AI-Enabled} FinTech B2B Invoice Management application using React, Java, and MySQL.
    \item Deployed a payment prediction model with \textbf{80\% accuracy} via \textbf{EDA} and \textbf{Feature engineering} using Python.
\end{bullets}
\sectionsep

\resumeHeading{\href{https://grapixi.netlify.app/}{GRAPIXI}}{Freelance}{Remote}{Jun 2021 - Aug 2021}
\begin{bullets}
    \item Employed \textbf{HTML, CSS, JavaScript} {\&} \textbf{jQuery} to built \textbf{responsive} portfolio with \textbf{cross-browser compatibility}.
    \item Led a team of \textbf{four} (TeamClover) \textbf{managing CI/CD workflows} for seamless updates on Netlify.
\end{bullets}
\sectionsep


%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}

\projectHeading{Sync Speak}{https://sync-speak.vercel.app/}{React.js, WebRTC, MongoDB}
\begin{bullets}
    \item Developed social audio app leveraging \textbf{WebRTC} {\&} \textbf{SocketIO} for \textbf{real-time} chat with an average \textbf{latency of 45-75ms}.
    \item Architectured \textbf{microservices} and implemented the \textbf{MVC} pattern for improved scalability and maintainability.
    \item Orchestrated \textbf{protected routes} using '\textbf{react-router-dom}' and efficient \textbf{global-state storage} using Redux.
    \item Integrated \textbf{Twilio API} for \textbf{OTP}-based authentication over sms /email to enhance security and user verification.
\end{bullets}
\sectionsep

\projectHeading{Health Vault}{https://drive.google.com/file/d/1lkFZ4CTtqBathC-tjjWjZTQndRRtOzoN/view?usp=sharing}{React.js, Solidity, Ethereum}
\begin{bullets}
    \item Proficiently engaged in Decentralized Healthcare, developing a Electronic Health Records Management platform on Ethereum Blockchain, solving \textbf{interoperability} and \textbf{privacy} among stakeholders.
    \item Built \textbf{easy interface} using \textbf{React} and ensured the integrity and availability of decentralized records via \textbf{IPFS}.
    \item Strengthened platform integrating \textbf{Aadhaar API} for \textbf{e-KYC} authentication, \textbf{countering DDoS} and \textbf{Sybil} attacks.
\end{bullets}
\sectionsep

\projectHeading{Cloud Drive}{https://cloud-drive-4uvf.onrender.com/}{EJS, Express.js, MongoDB}
\begin{bullets}
    \item Engineered a secure, \textbf{scalable} cloud storage for file management {\&} synchronization with direct relay to \textbf{S3 Bucket}.
    \item Designed dynamic user interfaces with \textbf{EJS} templates, enabling admin controls, search and \textbf{sharing} capabilities.
\end{bullets}
\sectionsep

% \projectHeading{Food Savers - Minimizing the food waste}{https://github.com/mrsayan/food-savers}{Team Project}
% {Best Beginner Team @ HackOn 2.0, Major League Hacking}
% \begin{bullets}
%     \item \textbf{Description: } Food Savers is an app designed to reduce food wastage by allowing communities to come together digitally to share food items \textbf{preventing avoidable food wastage}.
%     \item \textbf{Features: } Secure login using \textbf{Firebase authentication}, text and barcode recognition using Firebase Machine Learning Kit API, food recognition using Open Food facts API, personal virtual fridge, community sharing, messaging service, and \textbf{simple UI} design for easy navigation.
%     \item \textbf{Exposure: } \textit{Flutter (Dart), Firebase, Firestore, Cloud Messaging, Rest APIs}
% \end{bullets}
% \sectionsep

% \projectHeading{MEET-LINK}{https://github.com/mrsayan/meet-link}{Javascript, Webpack}
% \begin{bullets}
%     \item \textbf{Description: } Built and launched a \textbf{Dynamic URL} that \textbf{streamlined the process of joining Google Meet link} for students with weekly class schedules; increased student attendance by \textbf{40 percent}.
%     \item \textbf{Features: } Fetch faculty name and subject code as per the class schedule, option of selecting a section, enable users to upload timetable which will \textbf{sync with all users} in that section, \textbf{minimise search for links} before joining a class.
%     \item \textbf{Impact: } \textit{Have been used by more than \textbf{300+ Students} with over \textbf{25K views} within a month.}
% \end{bullets}
% \sectionsep

%--------------------------------------------------------------
%     Achievement
%--------------------------------------------------------------
\section{Achievements}
\begin{bullets}
    \item  \textbf{\href{https://drive.google.com/file/d/1PHLWF7olshOeVYCrIPq_-AS-QvxKBV9m/view?usp=sharing}{Google Hash Code:}} Points scored: \textit{20,92,461} , \textbf{\textit{ Global Rank 1735}} (\textit{Country Rank 488}).
    \item  \textbf{\href{https://www.codechef.com/users/mrsayan/}{Codechef:}} Max Rating: \textbf{5 star (2000)} , Best Performance: \textbf{\textit{Global Rank: 125}} in June Cook-Off 2021 Division 2
    \item Cleared \textbf{\href{https://www.hackerrank.com/certificates/4099d9ae927f}{Problem Solving ( \textit{Intermediate} )}} and \textbf{\href{https://www.hackerrank.com/certificates/5ce743e1535f}{Node Js ( \textit{Advanced} )}} assessment by \textbf{HackerRank}.
    \item 
    Qualified for \textbf{\href{https://drive.google.com/file/d/1nG47kEjyQut83Ep9Tz-li2tB_1fTugOQ/view?usp=sharing}{Level 2 in Flipkart GRiD 5.0}} - Health+ Track, the \textbf{\textit{only team}} from the college to do so.
    % \item Got accepted into \textbf{\textit{AWS Machine Learning Engineer Nanodegree}} program by Udacity
\end{bullets}
\sectionsep

%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
% \begin{skillList}
%     \singleItem{Technical:}{Java, Javascipt/Typescript, Solidity, SQLite, MongoDB, Redis, Express.js, React/Next.js, Truffle, Docker, AWS (S3, EC2), Git}
%     \\
%     \singleItem{Non-Technical:}{Teamwork, Leadership, Versatility, Problem Solving, Chess, Painting}
% \end{skillList}

% A more concise alternate 
\begin{skillList}
% \item{Technical:}
    % \\
    \doubleItem{Languages:}{Java, Javascript/TypeScript, Python, Solidity}%
    {Databases:}{MySQL, MongoDB, Redis, Prisma}
    \\
    \doubleItem{Technologies:}{React, Node.js, Express, Truffle, WebRTC, SocketIO, Postman }
    {Cloud:}{Linux, Docker, AWS (S3, EC2), Git Actions}%
    \\
    % \doubleItem{Softskills:}{Teamwork, Leadership, Versatility, Problem Solving, Chess, Painting}
    % {}{}%
    
\end{skillList}
\end{document}